Supplementary Materials And Methods

### 2020-11-05 Supplementary_mat_met.Rmd
tidyverse styling and validating code

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)-> sample_graph

find_node_perturbation(sample_graph, how = 2, cycle = 3, limit = 0.1)%>%
  as_tibble()%>%
  select(name, perturbation_efficiency, perturbed_count)

@@

@@

clashelwak <- read.table(clash_url, comment.char = "#", header = TRUE, skip = 1, stringsAsFactors = FALSE)

@@

```{r,  eval=FALSE}
#HG19
listEnsemblArchives()
listMarts(host = 'http://grch37.ensembl.org')
ensemblgrch37 = useMart(host='http://grch37.ensembl.org', 
                     biomart='ENSEMBL_MART_ENSEMBL',
                    dataset='hsapiens_gene_ensembl')
hg19 <- getBM(attributes = c("ensembl_transcript_id","ensembl_gene_id","chromosome_name", "start_position","end_position", "hgnc_symbol", "entrezgene_id", "strand" ), mart = ensemblgrch37)

@@

clashelwak <- clashelwak%>%
 separate(microRNA_name, c("Barcode", "Database", "mirna_name", "type"), sep = "_")%>%
  separate(mRNA_name, c("Ensembl_Gene_Id", "Ensembl_Transcript_Id", "Hugo_Symbol", "mRNA_Type"), sep = "_")

MiRNA releases are obtained from [miRBase](http://www.mirbase.org/ftp.shtml). In this step, release 21 (in Human genome 38) was downloaded.

```{r, eval=FALSE}
mirbase_url <- "ftp://mirbase.org/pub/mirbase/21/genomes/hsa.gff3"

read.table(mirbase_url, comment.char = "#")%>%
  filter(V3 != "miRNA_primary_transcript")%>%
  separate(V9, c("ID", "Alias", "Name", "Precusor"), sep = ";")%>%
  mutate(ID = substr(ID, 4, length(ID)), Alias = substr(Alias, 7, length(Alias)), Name = substr(Name, 6, length(Name)), Precusor = substr(Precusor, 14, length(Precusor)))%>%
  dplyr::select(chr= V1, start = V4, end = V5, strand = V7, ID, Alias, Name, Precusor)->mirbasehg38

@@

read_tsv(mirbase15_url, col_names = FALSE)%>%
  filter(startsWith(X2, "hsa"))%>%
  dplyr::select(mirna_ID = X2, mirbase_ID = X3)%>%
  inner_join(mirbasehg38%>% dplyr::select(ID, Name), by= c("mirbase_ID"= "ID"))%>%
  dplyr::select(mirbase_ID, Name)%>%
  distinct()%>%
  inner_join(clashelwak, by = c("mirbase_ID"= "Barcode"))%>%
  dplyr::select(Name, miRNA_seq, Ensembl_Gene_Id, Ensembl_Transcript_Id, Hugo_Symbol, mRNA_seq_extended, chimeras_decompressed, seed_type, seed_basepairs,folding_class, seq_ID, folding_energy, X5.UTR, CDS, X3.UTR)%>%
  inner_join(hg19, by = c("Ensembl_Gene_Id"= "ensembl_gene_id", "Ensembl_Transcript_Id"="ensembl_transcript_id", "Hugo_Symbol"="hgnc_symbol"))%>%
  mutate(region1 = ifelse(X5.UTR == "1", "5UTR", " "), region2= ifelse(X3.UTR == "1", "3UTR", " "),region3= ifelse(CDS =="1", "CDS", " "))%>%
  unite(region, c(region1, region2, region3), sep = "||")%>%
  dplyr::select(chromosome_name, start_position, end_position,strand, Hugo_Symbol, Ensembl_Gene_Id, Ensembl_Transcript_Id, mRNA_seq_extended, Name, miRNA_seq, seq_ID, seed_type,seed_basepairs, folding_class, folding_energy, region)%>%
  as_tibble() -> clashelwakfinal

@@

lift19 <- clashelwakfinal%>%
  dplyr::select(1,2,3)%>%
  unite(start_end, c("start_position", "end_position"), sep = "-")%>%
  mutate(Chromosome = paste0("chr",chromosome_name, ""))%>%
  unite(chromosome_name, c("Chromosome","start_end"), sep = ":")

write_tsv(lift19, "lift19.txt")

#After we searched this file in UCSC browser, the output loaded (lift19_del deleted regions on the HG38 genome build; hg38clashcomp new locations of the genes on HG38)

@@

lift19_del <- lift19_del%>%
  dplyr::filter(startsWith(chromosome_loc, "chr"))%>%
  separate(chromosome_loc, c("Chr", "End"), "-", remove = TRUE)%>%
  separate(Chr, c("Chr", "Start"), ":", remove = TRUE)

@@

clashelwakfinal <-clashelwakfinal%>%
  mutate(Chromosome = paste0("chr",chromosome_name, ""))%>%
  dplyr::anti_join(lift19_del, by = c("Chromosome"="Chr", "start_position"="Start", "end_position"="End"))

@@

clashelwakfinal <- clashelwakfinal%>% 
  bind_cols(hg38clash)

@@

clashelwakfinal <- clashelwakfinal%>%
  dplyr::mutate(Genom_build= rep("hg19"))

@@

clashelwakfinal%>% dplyr::select(cluster=seq_ID, chromosome = Chromosome, start_position, end_position, strand, hgnc_symbol = Hugo_Symbol, Ensembl_Gene_Id, Ensembl_Transcript_Id, target_seq = mRNA_seq_extended, miRNA= Name, miR_seq =miRNA_seq, seed_type, seed_type2= seed_basepairs, seed_type3= folding_class, Energy = folding_energy, HG38build_loc, Genom_build, region) -> clashelwakfinal

@@

```{r,  eval=FALSE}
clashelwakfinal%>%
  mutate(seed_type= ifelse (seed_type == "noncanonical_seed"& seed_type2 >4 &seed_type3=="I", paste0(seed_type2, "-mer"), seed_type),
         seed_type= ifelse (seed_type == "noncanonical_seed"& seed_type2 >4 &seed_type3=="II", paste0(seed_type2, "-mer_noncanonical"), seed_type), 
         seed_type= ifelse (seed_type == "noncanonical_seed"& seed_type2 >4 &seed_type3=="III", paste0(seed_type2, "-mer_noncanonical"), seed_type),
         seed_type= ifelse (seed_type == "noncanonical_seed"& seed_type2 >4 &seed_type3=="IV", paste0(seed_type2, "-mer_noncanonical"), seed_type),
         seed_type= ifelse (startsWith(seed_type, "no") ,"none", seed_type))%>%
  dplyr::select(-seed_type2, -seed_type3)->clashelwakfinal

@@

```{r,  eval=FALSE}
#HG18
listEnsemblArchives()
listMarts(host = 'may2009.archive.ensembl.org')
ensembl54 = useMart(host='may2009.archive.ensembl.org', 
                     biomart='ENSEMBL_MART_ENSEMBL',
                    dataset='hsapiens_gene_ensembl')

hg18 <- getBM(attributes = c("ensembl_transcript_id","ensembl_gene_id","chromosome_name", "start_position","end_position", "hgnc_symbol", "entrezgene", "strand" ), mart = ensembl54)
```

@@

```{r,  eval=FALSE}
clearclipfinal <- hg18%>%
  inner_join(clearclip, by= c("entrezgene"= "gene.id", "hgnc_symbol"= "gene.symbol"))%>%
  distinct()
```

@@

lift18 <- clearclipfinal%>%
  unite(start_end, c("start_position", "end_position"), sep = "-")%>%
  unite(location, c("chr","start_end"), sep = ":")%>%
  dplyr::select(location)

@@

deleted_lift18 <- deleted_lift18%>%
  dplyr::filter(startsWith(Chromosome_loc, "chr"))%>%
  separate(Chromosome_loc, c("Chr", "End"), "-", remove = TRUE)%>%
  separate(Chr, c("Chr", "Start"), ":", remove = TRUE)

@@

clearclipfinal <- clearclipfinal%>%
  dplyr::anti_join(deleted_lift18, by = c("chr"="Chr", "start_position"="Start", "end_position"="End"))

@@

clearclipfinal <- clearclipfinal%>% 
  bind_cols(hg38clearclip)

@@

clearclipfinal <- clearclipfinal%>%
  dplyr::mutate(Genom_build= rep("hg18"))

@@

clearclipfinal%>%
  dplyr::select(cluster=cluster.ID, chromosome = chr, start_position, end_position, strand = strand.y, hgnc_symbol, Ensembl_Gene_Id =ensembl_gene_id, Ensembl_Transcript_Id =ensembl_transcript_id, target_seq = target.map, miRNA, miR_seq = miR.map, seed_type = 'seed match', Energy = MFE, HG38build_loc, Genom_build, region) -> clearclipfinal

@@

```{r,  eval=FALSE}
data_frame(seed_type= c("5mer_1","5mer_2", "5mer_3", "6mer", "6mer.indel", "6mer.mm", "6mer_off.mm", "6merA1", "6merA1.indel", "6merA1.mm", "7merA1", "7merA1.indel", "7merA1.mm", "7merm8", "7merm8.indel", "7merm8,mm", "8mer", "8mer.indel", "8mer.mm", "NA" ),
           seed_type_com= c("5-mer", "5-mer_noncanonical", "5-mer_noncanonical", "6-mer", "6-mer_noncanonical", "6-mer_noncanonical", "6-mer_noncanonical", "6-merA1", "6-merA1_noncanonical","6-merA1_noncanonical", "7-merA1", "7-merA1_noncanonical","7-merA1_noncanonical", "7-mer-8m", "7-mer-8m_noncanonical", "7-mer-8m_noncanonical", "8-mer", "8-mer_noncanonical", "8-mer_noncanonical", "none" )) ->clipdata_seed

clearclipfinal%>%
  inner_join(clipdata_seed, by = "seed_type")%>%
  dplyr::select(1:11, seed_type = seed_type_com, Energy, HG38build_loc, Genom_build, region)-> clearclipfinal

@@

bind_rows(clashelwakfinal, clearclipfinal)%>%distinct() -> experimentalmirnagene

@@

```{r,  eval=FALSE}
experimentalmirnagene <- experimentalmirnagene%>%
  mutate(region2  = str_replace_all(region, "NA", ""), region3 = str_replace_all(region2, "\\|", ""), region = str_replace_all(region3, c("3'UTR"="3UTR", "5'UTR"="5UTR")))%>%
  dplyr::select(-region2, -region3)%>%
  mutate(region_effect = as.double(ifelse(region %in% c("3UTRCDS", "CDS3UTR", "5UTR3UTR", "CDS5UTR3UTR", "CDS3UTRintron"), "0.93", ifelse(region %in% c("CDS", "CDSintron"), "0.42", ifelse(region %in% c("3UTR","3UTRintron"), "0.84", ifelse(region %in% c("5UTR", "5UTRintron"), "0.01", ifelse(region %in% c("5UTRCDS", "CDS5UTR"), "0.42", ifelse(region %in% c("intron",""), "0.01", ifelse(region %in% c("exon_unclassified", ""), "0.2", NA)))))))))

@@

seed_type_effect <- data_frame( seed_type = c("5-mer", "5-mer_noncanonical", "6-mer", "6-mer_noncanonical", "6-merA1", "6-merA1_noncanonical", "7-mer", "7-mer_noncanonical", "7-merA1", "7-merA1_noncanonical", "7-mer-8m", "7-mer-8m_noncanonical", "8-mer", "8-mer_noncanonical", "9-mer", "9-mer_noncanonical", "none"),
                                seed_type_effect= c(0.05, 0.04, 0.07, 0.05, 0.07, 0.05, 0.23, 0.19, 0.19, 0.16, 0.25, 0.21, 0.43, 0.35, 0.43,0.35, 0.01)
                                )
experimentalmirnagene%>%
  inner_join(seed_type_effect, by= "seed_type") -> experimentalmirnagene
```

```{r}
readRDS("data/experimentalmirnagene.RDS")->experimentalmirnagene
experimentalmirnagene
```

>>>>

sample_graph <- priming_graph(minsamp, 
                              competing_count = Competing_expression, 
                              miRNA_count = miRNA_expression, 
                              aff_factor = c(energy, seed_type), 
                              deg_factor = region)

find_node_perturbation(sample_graph, 
                       how = 2, 
                       cycle = 3, 
                       limit = 0.1) %>%
  as_tibble() %>%
  select(name, perturbation_efficiency, perturbed_count)

@@

```{r, eval=FALSE, warning=FALSE, message=FALSE}

@@

clashelwak <- read_tsv(clash_url, comment = "#", skip = 1)

@@

```{r, eval=FALSE}
library(biomaRt)  #can be installed via BiocManager

#listMarts(host = 'http://grch37.ensembl.org') #HG19
ensemblgrch37 <- useMart(host='http://grch37.ensembl.org',
                         biomart='ENSEMBL_MART_ENSEMBL',
                         dataset='hsapiens_gene_ensembl')

hg19 <- getBM(attributes = c("ensembl_transcript_id", 
                             "ensembl_gene_id",
                             "chromosome_name", 
                             "start_position",
                             "end_position", 
                             "hgnc_symbol", 
                             "entrezgene_id", 
                             "strand" ), 
              mart = ensemblgrch37)
```

@@

```{r,  eval=FALSE}
clashelwak <- clashelwak %>%
  separate(microRNA_name, 
           c("Barcode", "Database", "mirna_name", "type"), 
           sep = "_") %>%
  separate(mRNA_name, 
           c("Ensembl_Gene_Id", "Ensembl_Transcript_Id", 
             "Hugo_Symbol", "mRNA_Type"), 
           sep = "_") %>%
  rename_with(~ str_replace(.,"\'","_"), contains("UTR"))
```

miRNA releases are obtained from [miRBase](http://www.mirbase.org/ftp.shtml). In this step, release 21 (in Human genome 38) was downloaded.

```{r, eval=FALSE, warning=FALSE, message=FALSE}
mirbase_url <- "ftp://mirbase.org/pub/mirbase/21/genomes/hsa.gff3"

mirbasehg38 <- read_tsv(mirbase_url, comment = "#", col_names = FALSE) %>%
  filter(X3 != "miRNA_primary_transcript") %>%
  separate(X9, c("ID", "Alias", "Name", "Precusor"), sep = ";") %>%
  mutate(ID = substr(ID, 4, length(ID)), 
         Alias = substr(Alias, 7, length(Alias)), 
         Name = substr(Name, 6, length(Name)), 
         Precusor = substr(Precusor, 14, length(Precusor))) %>%
  dplyr::select(chr = X1, start = X4, end = X5, strand = X7, ID, Alias, Name, Precusor)
```

@@

clashelwakfinal <- read_tsv(mirbase15_url, col_names = FALSE) %>%
  filter(str_starts(X2, "hsa")) %>%
  dplyr::select(mirna_ID = X2, mirbase_ID = X3) %>%
  inner_join(mirbasehg38 %>% dplyr::select(ID, Name), 
             by = c("mirbase_ID" = "ID")) %>%
  dplyr::select(mirbase_ID, Name) %>%
  distinct() %>%
  inner_join(clashelwak, by = c("mirbase_ID" = "Barcode")) %>%
  dplyr::select(Name, miRNA_seq, Ensembl_Gene_Id, Ensembl_Transcript_Id, 
                Hugo_Symbol, mRNA_seq_extended, chimeras_decompressed, 
                seed_type, seed_basepairs, folding_class, seq_ID, 
                folding_energy, `5_UTR`, CDS, `3_UTR`) %>%
  inner_join(hg19, by = c("Ensembl_Gene_Id" = "ensembl_gene_id", 
                          "Ensembl_Transcript_Id" = "ensembl_transcript_id", 
                          "Hugo_Symbol" = "hgnc_symbol")) %>% 
  mutate(region1 = ifelse(`5_UTR` == "1", "5UTR", " "), 
         region2 = ifelse(`3_UTR` == "1", "3UTR", " "), 
         region3 = ifelse(CDS == "1", "CDS", " ")) %>%
  unite(region, c(region1, region2, region3), sep = "||") %>% 
  dplyr::select(chromosome_name, start_position, end_position, strand, 
                Hugo_Symbol, Ensembl_Gene_Id, Ensembl_Transcript_Id, 
                mRNA_seq_extended, Name, miRNA_seq, seq_ID, seed_type, 
                seed_basepairs, folding_class, folding_energy, region) 
```

@@

clashelwakfinal %>%
  dplyr::select(1,2,3) %>%
  unite(start_end, c("start_position", "end_position"), sep = "-") %>%
  mutate(Chromosome = paste0("chr",chromosome_name, "")) %>%
  unite(chromosome_name, c("Chromosome","start_end"), sep = ":") %>% 
  write_tsv("lift19.txt",col_names = FALSE)

#After we uploaded this file to UCSC Liftover site, the output files  lift19_del (deleted regions on the HG38 genome build) and hg38clashcomp (new locations of the genes on HG38) were downloaded

@@

lift19_del <- lift19_del %>%
  dplyr::filter(startsWith(chromosome_loc, "chr")) %>%
  separate(chromosome_loc, c("Chr", "End"), "-", remove = TRUE) %>%
  separate(Chr, c("Chr", "Start"), ":", remove = TRUE)

@@

clashelwakfinal <-clashelwakfinal%>%
  mutate(Chromosome = paste0("chr",chromosome_name, "")) %>%
  dplyr::anti_join(lift19_del, by = c("Chromosome"="Chr",
                                      "start_position"="Start",
                                      "end_position"="End"))

@@

clashelwakfinal <- clashelwakfinal %>% 
  bind_cols(hg38clash)

@@

clashelwakfinal <- clashelwakfinal %>%
  dplyr::mutate(Genom_build= rep("hg19"))

@@

clashelwakfinal <- clashelwakfinal %>% 
  dplyr::select(cluster=seq_ID, 
                chromosome = Chromosome,
                start_position, end_position, strand,
                hgnc_symbol = Hugo_Symbol,
                Ensembl_Gene_Id, Ensembl_Transcript_Id,
                target_seq = mRNA_seq_extended,
                miRNA = Name,
                miR_seq = miRNA_seq,
                seed_type,
                seed_type2 = seed_basepairs,
                seed_type3 = folding_class,
                Energy = folding_energy,
                HG38build_loc, Genom_build, region)

@@

```{r,  eval=FALSE}
clashelwakfinal <- clashelwakfinal %>%
  mutate(seed_type= ifelse (seed_type == "noncanonical_seed" & seed_type2 >4 & seed_type3=="I", 
                            paste0(seed_type2, "-mer"), 
                            seed_type),
         seed_type= ifelse (seed_type == "noncanonical_seed" & seed_type2 >4 & seed_type3=="II", 
                            paste0(seed_type2, "-mer_noncanonical"), 
                            seed_type), 
         seed_type= ifelse (seed_type == "noncanonical_seed" & seed_type2 >4 & seed_type3=="III", 
                            paste0(seed_type2, "-mer_noncanonical"), 
                            seed_type),
         seed_type= ifelse (seed_type == "noncanonical_seed" & seed_type2 >4 & seed_type3=="IV", 
                            paste0(seed_type2, "-mer_noncanonical"), 
                            seed_type),
         seed_type= ifelse (startsWith(seed_type, "no") ,
                            "none", 
                            seed_type))%>%
  dplyr::select(-seed_type2, -seed_type3)

@@

```{r,  eval=FALSE}
#HG18

#listMarts(host = 'http://may2009.archive.ensembl.org')

ensembl54 <- useMart(biomart='ENSEMBL_MART_ENSEMBL',
                    dataset='hsapiens_gene_ensembl',
                    host='may2009.archive.ensembl.org')
ensembl54 <- useEnsembl(biomart = 'genes', 
                       dataset = 'hsapiens_gene_ensembl',
                       version = 54)
listMarts(host="may2009.archive.ensembl.org")
useMart("ensembl",host="may2009.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")
httr_config <- httr::config(ssl_cipher_list = "DEFAULT@SECLEVEL=1")

mart <- useEnsembl(biomart = "ensembl", 
                   dataset = "hsapiens_gene_ensembl", 
                   version = "54")

hg18 <- getBM(attributes = c("ensembl_transcript_id",
                             "ensembl_gene_id",
                             "chromosome_name", 
                             "start_position",
                             "end_position", 
                             "hgnc_symbol", 
                             "entrezgene", 
                             "strand" ), 
              mart = ensembl54)
```

@@

```{r,  eval=FALSE}
clearclipfinal <- hg18 %>%
  inner_join(clearclip, by= c("entrezgene"= "gene.id", 
                              "hgnc_symbol"= "gene.symbol")) %>%
  distinct()
```

@@

lift18 <- clearclipfinal %>%
  unite(start_end, c("start_position", "end_position"), sep = "-") %>%
  unite(location, c("chr","start_end"), sep = ":") %>%
  dplyr::select(location)

@@

deleted_lift18 <- deleted_lift18 %>%
  dplyr::filter(startsWith(Chromosome_loc, "chr")) %>%
  separate(Chromosome_loc, c("Chr", "End"), "-", remove = TRUE) %>%
  separate(Chr, c("Chr", "Start"), ":", remove = TRUE)

@@

clearclipfinal <- clearclipfinal %>%
  dplyr::anti_join(deleted_lift18, by = c("chr"="Chr", 
                                          "start_position"="Start", 
                                          "end_position"="End"))

@@

clearclipfinal <- clearclipfinal %>% 
  bind_cols(hg38clearclip)

@@

clearclipfinal <- clearclipfinal %>%
  dplyr::mutate(Genom_build= rep("hg18"))

@@

clearclipfinal %>%
  dplyr::select(cluster=cluster.ID, chromosome = chr, start_position, 
                end_position, strand = strand.y, hgnc_symbol, 
                Ensembl_Gene_Id =ensembl_gene_id, 
                Ensembl_Transcript_Id =ensembl_transcript_id, 
                target_seq = target.map, miRNA, 
                miR_seq = miR.map, 
                seed_type = 'seed match', Energy = MFE, 
                HG38build_loc, Genom_build, region) -> clearclipfinal

@@

```{r,  eval=FALSE}
clipdata_seed <- data_frame(seed_type= c("5mer_1","5mer_2", "5mer_3", "6mer", "6mer.indel", "6mer.mm", "6mer_off.mm", "6merA1", "6merA1.indel", "6merA1.mm", "7merA1", "7merA1.indel", "7merA1.mm", "7merm8", "7merm8.indel", "7merm8,mm", "8mer", "8mer.indel", "8mer.mm", "NA" ),
           seed_type_com= c("5-mer", "5-mer_noncanonical", "5-mer_noncanonical", "6-mer", "6-mer_noncanonical", "6-mer_noncanonical", "6-mer_noncanonical", "6-merA1", "6-merA1_noncanonical","6-merA1_noncanonical", "7-merA1", "7-merA1_noncanonical","7-merA1_noncanonical", "7-mer-8m", "7-mer-8m_noncanonical", "7-mer-8m_noncanonical", "8-mer", "8-mer_noncanonical", "8-mer_noncanonical", "none" ))

clearclipfinal <- clearclipfinal %>%
  inner_join(clipdata_seed, by = "seed_type") %>%
  dplyr::select(1:11, seed_type = seed_type_com, Energy, HG38build_loc, Genom_build, region)

@@

experimentalmirnagene <- bind_rows(clashelwakfinal, clearclipfinal) %>%
  distinct()  
```

@@

```{r,  eval=FALSE}
experimentalmirnagene <- experimentalmirnagene %>%
  mutate(region2 = str_replace_all(region, "NA", ""), 
         region3 = str_replace_all(region2, "\\|", ""), 
         region = str_replace_all(region3, c("3'UTR" = "3UTR", "5'UTR" = "5UTR"))) %>%
  dplyr::select(-region2, -region3) %>%
  mutate(region_effect = case_when(
    region %in% c("3UTRCDS", "CDS3UTR", "5UTR3UTR", "CDS5UTR3UTR", "CDS3UTRintron") ~ "0.93",
    region %in% c("CDS", "CDSintron") ~ "0.42",
    region %in% c("3UTR", "3UTRintron") ~ "0.84",
    region %in% c("5UTR", "5UTRintron") ~ "0.01",
    region %in% c("intron", "") ~ "0.01",
    region %in% c("exon_unclassified", "") ~ "0.2",
    TRUE ~ NA
  ) %>% 
    mutate(region_effect = as.double(region_effect))
```

@@

seed_type_effect <- data_frame( seed_type = c("5-mer", "5-mer_noncanonical", "6-mer", "6-mer_noncanonical", "6-merA1", "6-merA1_noncanonical", "7-mer", "7-mer_noncanonical", "7-merA1", "7-merA1_noncanonical", "7-mer-8m", "7-mer-8m_noncanonical", "8-mer", "8-mer_noncanonical", "9-mer", "9-mer_noncanonical", "none"),
                                seed_type_effect= c(0.05, 0.04, 0.07, 0.05, 0.07, 0.05, 0.23, 0.19, 0.19, 0.16, 0.25, 0.21, 0.43, 0.35, 0.43,0.35, 0.01)
                                )
experimentalmirnagene <- experimentalmirnagene %>%
  inner_join(seed_type_effect, by= "seed_type")
```

```{r}
experimentalmirnagene <- readRDS("data/experimentalmirnagene.RDS")
experimentalmirnagene
```
